KidsAIR: merge health datasets

### 2020-03-30 exposure_initial_analysis.Rmd
ambient data updates

---
title: "KidsAIR: initial exposure analysis"
author: "Ethan Walker"
date: "Started 2 Feb 2020, Updated 26 March 2020"
output: pdf_document
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
```

@@

sums_rolling_pm_data <- read_rds("Output/sums_rolling_pm_data.rds")
```

@@

pm_sums_results <- lmer(log(pm_mean_sampling_day) ~ temp_perc_25_2level + 
                              (1 | home), data = analysis_data)
summary(pm_sums_results)
tidy(pm_sums_results)
plot(pm_sums_results, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(pm_sums_results), main = "QQ Plot")
```

@@

pm_sums_results <- lm(log(pm_mean_sampling_period) ~ sums_mean_sampling_period_5, 
                      data = analysis_data)
summary(pm_sums_results)
tidy(pm_sums_results)
plot(pm_sums_results, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(pm_sums_results), main = "QQ Plot")
```

@@

cor.test(analysis_data$temp_c_sums, analysis_data$pm_rolling_20, method = "spearman")
pm_sums_model <- lmer(log(pm_rolling_20) ~ temp_c_sums_5 + (1 | home), 
                      data = analysis_data)

summary(pm_sums_model)
tidy(pm_sums_model)
exp((0.146291)-1)*100
plot(pm_sums_model, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(pm_sums_model), main = "QQ Plot")

@@

# SUMs - events per sampling day - KEEP WORKING ON THIS
```{r}
sums_temp_change <- sums_rolling_pm_data %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area, home, sample_date) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>% 
  mutate(time_diff = (lead(datetime_sums) - datetime_sums)/60) %>% 
  mutate(lead_temp = if_else(time_diff < 20, lead(temp_c_sums, 4), lead(temp_c_sums)),
         lead_temp = if_else(time_diff > 25, 999, lead_temp)) %>% 
  replace_with_na(replace = list(lead_temp = 999)) %>% 
  mutate(temp_diff = lead_temp - temp_c_sums,
         temp_diff_abs = abs(lead_temp - temp_c_sums),
         # change temp in the following line
         temp_diff_check = if_else(temp_diff >= 8, 1, 0),
         heat_event = if_else(temp_diff_check == 1 & lag(temp_diff_check) == 1, 0,
                              temp_diff_check),
         heat_event = if_else(is.na(temp_diff_check), 1,
                              heat_event)) %>% 
  ungroup() %>% 
  mutate(sample_date = as.character(sample_date)) %>% 
  group_by(area, home, sample_date) %>% 
  mutate(sums_events = sum(heat_event, na.rm = TRUE),
         sums_events_cat = cut(sums_events, breaks = c(0, 5, 50),
                           labels = c("<4", "4+"),
                                 right = FALSE)) %>% 
  ungroup() %>% 
  arrange(area, home, sample_date)

@@

pm_sums_model <- lmer(mean_pm ~ sums_events + (1 | home), data = sums_temp_change)
pm_sums_model <- lmer(log(pm_mean_daily) ~ sums_events + (1 | home), data = sums_temp_change)

summary(pm_sums_model)
#exp((0.146291)-1)*100
plot(pm_sums_model, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(pm_sums_model), main = "QQ Plot")

pm_sums_plot <- pm_sums_events_joined %>% 
  filter(!is.na(sums_events)) %>% 
  ggplot() + 
    geom_boxplot(aes(sums_events_cat, log(mean_pm))) +
    theme_minimal()
pm_sums_plot
```

>>>>

---
title: "KidsAIR: initial exposure analysis"
author: "Ethan Walker"
date: "Started 2 Feb 2020, Updated 30 March 2020"
output: pdf_document
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(ggmap)
```

@@

sums_rolling_pm_data <- read_rds("Output/sums_rolling_pm_data.rds")

health_exposure_data_sampling_day <- read_rds("Output/health_exposure_data_sampling_day.rds")
```

@@

table(analysis_data$temp_perc_30_2level)
median(analysis_data$temp_perc_30, na.rm = TRUE)

pm_sums_results <- lmer(log(pm_mean_sampling_day) ~ temp_perc_30_2level + 
                              (1 | home), data = analysis_data)
pm_sums_results <- lmer(pm_mean_sampling_day ~ temp_perc_30_2level + 
                              (1 | home), data = analysis_data)
summary(pm_sums_results)
tidy(pm_sums_results)
plot(pm_sums_results, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(pm_sums_results), main = "QQ Plot")
```

@@

pm_sums_results <- lm(log(pm_mean_sampling_period) ~ sums_mean_sampling_period_5, 
                      data = analysis_data)
pm_sums_results <- lm(pm_mean_sampling_period ~ sums_mean_sampling_period_5, 
                      data = analysis_data)
summary(pm_sums_results)
tidy(pm_sums_results)
plot(pm_sums_results, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(pm_sums_results), main = "QQ Plot")
```

@@

cor.test(analysis_data$temp_c_sums, analysis_data$pm_rolling_20, method = "spearman")
pm_sums_model <- lmer(log(pm_rolling_20) ~ temp_c_sums_5 + (1 | home), 
                      data = analysis_data)
pm_sums_model <- lmer(pm_rolling_20 ~ temp_c_sums_5 + (1 | home), 
                      data = analysis_data)

summary(pm_sums_model)
tidy(pm_sums_model)
exp((0.1496794)-1)*100
plot(pm_sums_model, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(pm_sums_model), main = "QQ Plot")

@@

# SUMs - events per sampling day 
```{r}
sums_temp_change <- sums_rolling_pm_data %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area, home, sampling_day) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>% 
  group_by(area, home, sampling_day) %>% 
  mutate(time_diff = (lead(datetime_sums) - datetime_sums)) %>% 
  mutate(lead_temp = if_else(time_diff < 20, lead(temp_c_sums, 4), lead(temp_c_sums)),
         lead_temp = if_else(time_diff > 25, 999, lead_temp)) %>% 
  replace_with_na(replace = list(lead_temp = 999)) %>% 
  mutate(temp_diff = lead_temp - temp_c_sums,
         # change temp in the following line
         temp_diff_check = if_else(temp_diff >= 5, 1, 0),
         heat_event = if_else(temp_diff_check == 1 & lag(temp_diff_check) == 1, 0,
                              temp_diff_check),
         heat_event = if_else(is.na(temp_diff_check), 1,
                              heat_event)) %>% 
  group_by(area, home, sampling_day) %>% 
  mutate(sums_events = sum(heat_event, na.rm = TRUE),
         sums_events_cat = cut(sums_events, breaks = c(0, 2, 50),
                           labels = c("<2", "2+"),
                                 right = FALSE)) %>% 
  distinct(sampling_day, .keep_all = TRUE) %>% 
  ungroup() %>% 
  select(area:pm_rolling_20, sums_mean_winter:sums_mean_sampling_period,
         time_diff:sums_events_cat) %>% 
  arrange(area, home, sample_date)

@@

pm_sums_model <- lmer(pm_mean_sampling_day ~ sums_events_cat + 
                        (1 | home), data = sums_temp_change)
pm_sums_model <- lmer(log(pm_mean_sampling_day) ~ sums_events_cat + 
                        (1 | home), data = sums_temp_change)

summary(pm_sums_model)
tidy(pm_sums_model)
#exp((0.146291)-1)*100
plot(pm_sums_model, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(pm_sums_model), main = "QQ Plot")

pm_sums_plot <- sums_temp_change %>% 
  filter(!is.na(sums_events)) %>% 
  ggplot() + 
    geom_boxplot(aes(sums_events_cat, log(pm_mean_sampling_day))) +
    theme_minimal()
pm_sums_plot
```

### 2020-03-30 merge_health_datasets.Rmd
ambient data updates

health_exposure_data_sampling_day <- health_data_merged %>% 
  mutate(winter_id = as.character(winter_id)) %>% 
  left_join(exposure_analysis_data_medium,
            by = c("area", "home", "home_winter_id", "winter_id", "treatment",
                   "child_id_num", "sampling_day"))

>>>>

health_exposure_data_sampling_day <- health_data_merged %>% 
  select(-pm_mean_sampling_day, -pm_mean_sampling_period, day_of_week) %>% 
  mutate(winter_id = as.character(winter_id)) %>% 
  left_join(exposure_analysis_data_medium,
            by = c("area", "home", "home_winter_id", "winter_id", "treatment",
                   "child_id_num", "sampling_day"))
